Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 algorithm_regret.tex
Revert "marked using bcedit"
Reverting 3 of bangrui's commits that added in an extra term to the
regret guarantee that is polynomial in T.  Rather than making this
change, we are going to change the proof so that we get rid of this
term.

This reverts commit a6ab7f1767f177a8a9e980614ab0537c83b18402.

Adding all four types of regret terms,
and substituting 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most
$
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \frac{\ARMNUM \MAXR d}{T}
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
= 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
\end{emptyextraproof}

>>>>

Adding all four types of regret terms,
and substituting 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most
$
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \frac{\ARMNUM \MAXR d}{T}
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
= 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \log^2(T) + \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
\end{emptyextraproof}

### 2018-06-06 introduction.tex
Revert "marked using bcedit"
Reverting 3 of bangrui's commits that added in an extra term to the
regret guarantee that is polynomial in T.  Rather than making this
change, we are going to change the proof so that we get rid of this
term.

This reverts commit a6ab7f1767f177a8a9e980614ab0537c83b18402.

\begin{theorem} \label{thm:main-intro}
Assume that for each arm, at least a constant fraction \MinProb
of the population likes this arm best,
and let \TieDensity be a measure of the ``density of near-ties''
between agents' arm preferences
(in a sense made precise in Section~\ref{sec:prob}).
There is a policy that achieves expected 
    cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \bcedit{\ARMNUM \log^2(T)} + \TieDensity \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
\end{theorem}

>>>>

\begin{theorem} \label{thm:main-intro}
Assume that for each arm, at least a constant fraction \MinProb
of the population likes this arm best,
and let \TieDensity be a measure of the ``density of near-ties''
between agents' arm preferences
(in a sense made precise in Section~\ref{sec:prob}).
There is a policy that achieves expected 
    cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^2(T) + \TieDensity \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
\end{theorem}

### 2018-06-06 result_discussion.tex
Revert "marked using bcedit"
Reverting 3 of bangrui's commits that added in an extra term to the
regret guarantee that is polynomial in T.  Rather than making this
change, we are going to change the proof so that we get rid of this
term.

This reverts commit a6ab7f1767f177a8a9e980614ab0537c83b18402.

\begin{theorem} \label{rst:regret}
For any time horizon $T$, the expected cumulative regret for
Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
above by 
    $O \left(\ARMNUM \cdot \e^{2/\MinProb} + \bcedit{\ARMNUM \log^2(T)}+ \TieDensity \ARMNUM \log^3(T) \right)$.
\end{theorem}

>>>>

\begin{theorem} \label{rst:regret}
For any time horizon $T$, the expected cumulative regret for
Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
above by 
    $O \left(\ARMNUM \cdot \e^{2/\MinProb} + \ARMNUM \log^2(T)+ \TieDensity \ARMNUM \log^3(T) \right)$.
\end{theorem}
